---
title: "Cuckoo Search Super Learner"
output: html_notebook
---


##Importing Package
required package:
*CVXR
*furrr
*tidyverse
*progress
```{r}
library(dplyr)
library(mlr)
library(SuperLearner)
```

##Source Files
Sourcce files are downloaded from github
```{r}
site="https://raw.githubusercontent.com/gdito7/SLcuckoo/master/"
source(paste0(site,"SL_mlr.R"))
source(paste0(site,"cons_ls.R"))
source(paste0(site,"new_metalearner.R"))
source(paste0(site,"SL_Adds_on.R"))
source(paste0(site,"r_mcs.R"))
source(paste0(site,"base_learner.R"))
```

## Data
Data are downloaded from github
```{r message=FALSE}
files_github=function(site,name_file){
  paste0(site,name_file)
}
site_files="https://raw.githubusercontent.com/gdito7/SLcuckoo/master/dataset/"
name_files=c("Breast%20Cancer.csv","Dermatology.csv","Heart%20Cleaveland.csv",
             "heart-statlog.csv","Hepatitis.csv","Lung%20Cancer.csv",
             "lymphography.csv","Pima%20Indian%20diabetes.csv")
list_files=files_github(site_files,name_files)

dta=purrr::map(list_files[-c(2,6,7)],function(lf){
  readr::read_csv(lf)
}
)

```
In below we are deciding the target of data
```{r}
targets=c("Class","class","Num","class"
          ,"y","class","class","Outcome")
targets=targets[-c(2,6,7)]
postive_class=c("recurrence-events","sick",
                "present","die",1)
names_data=c("Breast Cancer","Dermatology","Heart Cleaveland",
             "heart-statlog","Hepatitis.csv","Lung Cancer",
             "lymphography","Pima Indian diabetes")
names_data=names_data[-c(2,6,7)]

```
The codes are for fix small number category
```{r}
dta_fin=purrr::map(seq_along(dta), 
                   function(i){
                     res=dta[[i]]%>%mutate(!!targets[i]:=
                                                 ifelse(get(targets[i])==
                                                          postive_class[i],1,0))%>%
                       mutate_if(is.character,factor)%>%na.omit
                     
                     res=res%>%mutate_if(is.factor,function(k){
                       prp=k%>%table%>%prop.table%>%as.vector%>%sort
                       if(any(prp<0.1)){
                         prp_crit=which(prp<0.1)
                         chs=length(prp_crit)
                         
                         if(sum(prp[prp_crit])<0.1){
                           prp_crit=which(prp>0.1)
                           chs=1
                           prp_chs=prp[prp_crit[chs]]
                           forcats::fct_lump(k,prop=prp_chs)
                         }else{
                           prp_chs=prp[prp_crit[chs]]
                       forcats::fct_lump(k,prop=prp_chs)
                         }
                       }else{
                         k
                       }
                       }
                       )
                     class(res)="data.frame"
                     colnames(res)=make.names(colnames(res))
                     return(res)
                   }
)

```

## Define Base Learner
```{r}
configureMlr(show.learner.output = FALSE, show.info = FALSE)

base1 = c("classif.ctree",
          "classif.C50","classif.J48","classif.rpart","classif.naiveBayes",
          "classif.nnet","classif.logreg","classif.OneR","classif.IBk")

base_lrn1=stringr::str_c(base1,"_1")

```
## Define function Cuckoo Search Super Learner
```{r}
result_SL2=function(j){
band_cont=list(par11=c(0.05,0.99),par31=c(0.01,0.5),par51=c(0,1000),
               par62=c(0.0001,0.5))
band_disc=list(par12=c(5,150),par13=c(1,100),par21=c(1,100),
               par32=c(1,100),
               par41=c(5,150),par42=c(1,30),par61=c(1,30),
               par81=c(1,100),par91=c(2,100))

name_bin_band=c("par22","meta1","meta2",stringr::str_c("base_learner",1:9))


cuckoo_SL=function(par11,par12,par13,par21,par22,par31,par32,
         par41,par42,par51,par61,par62,par81,par91,meta1,meta2,...)
{

base_param=list(
  ctree=list(testtype="Bonferroni",
             mincriterion=par11,
             minsplit=par12,
             minbucket=round(par12/3),
             maxdepth=par13)
  ,
  C50=list(rules=F,trials=par21,winnow=as.logical(par22),
           fuzzyThreshold=TRUE,
           earlyStopping=T)
  ,
  J48=list(C=par31,M=par32)
  ,
  rpart=list(minsplit = par41,
             minbucket = round(par41/3),
             maxdepth = par42)
  ,
  naiveBayes=list(laplace=par51)
  ,
  nnet=list(size=par61,
            decay=par62),
  logreg=list(model=T),
  OneR=list(B=par81),
  IBk=list(K=par91)
)
SL_base1save=list()
for(i in seq_along(base1)){
  SL_base1=  create.Learner("SL.mlr",
                            params = list(learner=base1[i],
                                          par.vals= base_param[i]),
                            name_prefix = base1[i])
  SL_base1save[[i]]=SL_base1
}


nbase=c(...)
if(all(nbase==0)){
  nbase[sample(seq_along(nbase),1)]=1
}

lbl=nbase*seq_along(base_lrn1)
base_lrn2=base_lrn1[lbl[lbl!=0]]

metas=c(meta1,meta2)
if(any(duplicated(metas))){
  metas[sample(seq_along(metas),1)]=ifelse(
    metas[sample(seq_along(metas),1)]==1,0,1)
}
   

meta_lrn=c("method_consLS","method_NNRidge")
meta_lrn2=meta_lrn[metas[metas!=0]]
modSL2=function(Ytrain,Xtrain){

   SuperLearner(Y=Ytrain,X=Xtrain,family = binomial(),
               SL.library = base_lrn2,method=meta_lrn2,
               verbose = F,
               cvControl = list(V = 10L,
                                stratifyCV = FALSE,
                                shuffle = TRUE))

}



  dta_SL=SL_crossval(dta_fin[[j]],targets[j])
  
#  tictoc::tic("Super Learner")
  #tictoc::tic(stringr::str_c("Super Learner without ",base1[c(6,8)]))
  trainSL2=SL_train(modSL2,dta_SL,verbose = F)
#  tictoc::toc()
  SLperformance(trainSL2,measureACC,"all")

}

opt_cuckoo_SL=r_mcs(cuckoo_SL,cont_bnd = band_cont,disc_bnd = band_disc,
      name_bin_bnd = name_bin_band,n=7,alpha=1,iter_max = 50,
      primary_out = 1,save=T,save_files=paste0(names_data[j],"_mcs_res.rds"))

}
```

## Train the first data: Breast Cancer
```{r}
tictoc::tic()
set.seed(21)
res_cuckooSL=result_SL2(1)
tictoc::toc()
saveRDS(res_cuckoo,file =paste0(names_data[1],"_final_CSSL.rds"))
```
====================================================================================

## Resuming
### Define function Cuckoo Search Super Learner
```{r}
source(paste0(site,"resume_rmcs.R"))
result_SL2_resume=function(j){

cuckoo_SL=function(par11,par12,par13,par21,par22,par31,par32,
         par41,par42,par51,par61,par62,par81,par91,meta1,meta2,...)
{

base_param=list(
  ctree=list(testtype="Bonferroni",
             mincriterion=par11,
             minsplit=par12,
             minbucket=round(par12/3),
             maxdepth=par13)
  ,
  C50=list(rules=F,trials=par21,winnow=as.logical(par22),
           fuzzyThreshold=TRUE,
           earlyStopping=T)
  ,
  J48=list(C=par31,M=par32)
  ,
  rpart=list(minsplit = par41,
             minbucket = round(par41/3),
             maxdepth = par42)
  ,
  naiveBayes=list(laplace=par51)
  ,
  nnet=list(size=par61,
            decay=par62),
  logreg=list(model=T),
  OneR=list(B=par81),
  IBk=list(K=par91)
)
SL_base1save=list()
for(i in seq_along(base1)){
  SL_base1=  create.Learner("SL.mlr",
                            params = list(learner=base1[i],
                                          par.vals= base_param[i]),
                            name_prefix = base1[i])
  SL_base1save[[i]]=SL_base1
}


nbase=c(...)
if(all(nbase==0)){
  nbase[sample(seq_along(nbase),1)]=1
}

lbl=nbase*seq_along(base_lrn1)
base_lrn2=base_lrn1[lbl[lbl!=0]]

metas=c(meta1,meta2)
if(any(duplicated(metas))){
  metas[sample(seq_along(metas),1)]=ifelse(
    metas[sample(seq_along(metas),1)]==1,0,1)
}
   

meta_lrn=c("method_consLS","method_NNRidge")
meta_lrn2=meta_lrn[metas[metas!=0]]
modSL2=function(Ytrain,Xtrain){

   SuperLearner(Y=Ytrain,X=Xtrain,family = binomial(),
               SL.library = base_lrn2,method=meta_lrn2,
               verbose = F,
               cvControl = list(V = 10L,
                                stratifyCV = FALSE,
                                shuffle = TRUE))

}



  dta_SL=SL_crossval(dta_fin[[j]],targets[j])
  
#  tictoc::tic("Super Learner")
  #tictoc::tic(stringr::str_c("Super Learner without ",base1[c(6,8)]))
  trainSL2=SL_train(modSL2,dta_SL,verbose = F)
#  tictoc::toc()
  SLperformance(trainSL2,measureACC,"all")

}

opt_cuckoo_SL=resume_rmcs(rmcs_files=paste0(names_data[j],"_mcs_res.rds"),cuckoo_SL,cont_bnd = band_cont,disc_bnd = band_disc,
      name_bin_bnd = name_bin_band,n=7,alpha=1,iter_max = 50,
      primary_out = 1,save=T,save_files=paste0(names_data[j],"_mcs_res.rds"))

}


```
### Train the first data: Breast Cancer```
```{r}
tictoc::tic()
set.seed(21)
res_cuckooSL=result_SL2_resume(1)
tictoc::toc()
saveRDS(res_cuckoo,file =paste0(names_data[1],"_final_CSSL.rds"))


```

